Model validation plots

### 2021-05-13 doc/validate_models.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
## target knits Rmds in their own session, so load libraries here.
source(here::here("packages.R"))
library(gratia)
```

```{r load-targets}
withr::with_dir(here(),{
  tar_load(c(s_cf, s_1ha, g_cf, g_1ha, f_cf, f_1ha))
  })
```

@@

```{r echo=TRUE}
par(mfrow = c(2,2))
#histogram
plot(density(qresid(s_cf)))
#QQ plot
qqnorm(qresid(s_cf)); qqline(qresid(s_cf))
#Fitted vs. residuals
scatter.smooth(predict(s_cf, type = "response"), qresid(s_cf), col = "grey")
```
### Fragments

@@

@@

## Growth
### Continuous Forest
```{r}
summary(g_cf)
```

@@

@@

@@

@@

<details><summary>Reproducibility receipt</summary>

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
## target knits Rmds in their own session, so load libraries here.
library(targets)
library(statmod)
library(tidyverse)
library(gratia)
```

```{r load-targets}
withr::with_dir(here::here(),{
  tar_load(c(s_cf, s_1ha, g_cf, g_1ha, f_cf, f_1ha))
  })
```

@@

```{r}
draw(s_cf)
```

```{r echo=TRUE}
par(mfrow = c(2,2))
#histogram
plot(density(qresid(s_cf)))
#QQ plot
qqnorm(qresid(s_cf)); qqline(qresid(s_cf))
#Fitted vs. residuals
scatter.smooth(predict(s_cf, type = "response"), qresid(s_cf), col = "grey")
```

@@

```{r}
draw(s_1ha)
```

@@

## Growth

```{r}
summary(g_cf)
```

```{r}
draw(g_cf)
```

@@

```{r}
draw(g_1ha)
```

@@

```{r}
summary(f_cf)
```

```{r}
draw(f_cf)
```

@@

```{r}
summary(f_1ha)
```

```{r}
draw(f_1ha)
```

@@

<details>

<summary>

Reproducibility receipt

</summary>
